---
title: "Flags"
author: "GP SINGH"
date: "February 6, 2016"
output: html_document
---



### The dataset Flags is chosen from UCI Machine Learning Repository.





Reading the data from repository and creating a data frame




```{r}



y<- "https://archive.ics.uci.edu/ml/machine-learning-databases/flags/flag.data"

x <- read.table(y, header = FALSE, sep = ",")
```




Assigning names to the dataset attributes

```{r}




names(x) <- c("country", "landmass", "zone", "area", "population", "language", 
              "religion", "bars", "stripes", "colors", "red", "green", "blue",
              "gold", "white", "black", "orange","mainhue", "circles", "crosses", 
              "saltires", "quarters", "sunstars", "crescents", "triangle", "icon",
              "animate", "text", "topleft", "botright")
```




Create a subset of dataset with value of landmass chosen 1, 2 and 3. There might be different scenarios for selection we can choose for the dataset, I am focussing on the landmasses
N.America, S.America and Europe



N.America = 1
S.America = 2
Europe = 3


```{r}
set1 <- subset(x, landmass == 1 | landmass == 2 | landmass == 3)
```




Set 1 consists of all the information about the N. American, S.American and Europe landmasses. Set 1 has 30 attributes same as the original dataset.
The dataset is furthered filtered by their attributes. The information about the flags and their description is omitted. The land dataset is oriented towards languages,
population and religion of theses three landmasses. Again according to the analytical 
requirements, we can select the attributes we wish to consider for analysis.




```{r}



land <- set1[c(1:83), 1:7]
str(land)


```



Dimension of our new dataset

```{r}
dim(land)

```




Frequency of data distribution among three landmasses.


```{r}
table(land$landmass)

```


Subsetting and statistic

```{r}
NAm <- subset(land, landmass==1)


#population in round millions for N.America landmass
mean(NAm$population)
```